\newglossaryentry{gnss}{
  type=\acronymtype,
  name={GNSS},
  description={Global navigation satellite system},
  first={global navigation satellite system (GNSS)},
  sort={GNSS},
  long={global navigation satellite system},
  short={GNSS}
}

\newglossaryentry{dgnss}{
  type=\acronymtype,
  name={DGNSS},
  description={Differential GNSS},
  first={DGNSS (Differential GNSS)},
  sort={DGNSS},
  long={Differential GNSS},
  short={DGNSS}
}

\newglossaryentry{iot}{
  type=\acronymtype,
  name={IoT},
  description={Internet of things},
  first={internet of things (IoT)},
  sort={IoT},
  long={internet of things},
  short={IoT}
}

\newglossaryentry{rt}{
  type=\acronymtype,
  name={RT},
  description={Rayleigh-taylor},
  first={Rayleigh-Taylor (RT)},
  sort={RT},
  long={Rayleigh-Taylor},
  short={RT}
}

\newglossaryentry{ha}{
  type=\acronymtype,
  name={HA},
  description={High accuracy},
  first={high-accuracy (HA)},
  sort={HA},
  long={high accuracy},
  short={HA}
}

\newglossaryentry{mm}{
  type=\acronymtype,
  name={MM},
  description={Mass market},
  first={Mass-market (MM)},
  sort={MM},
  long={mass market},
  short={MM}
}


\newglossaryentry{aoa}{
  type=\acronymtype,
  name={AoA},
  description={Angle of arrival},
  first={angle of arrival (AoA)},
  sort={AoA},
  long={angle of arrival},
  short={AoA}
}

\newglossaryentry{pvt}{
  type=\acronymtype,
  name={PVT},
  description={Position, velocity and time},
  first={PVT (position, velocity and time)},
  sort={PVT},
  long={position, velocity and time},
  short={PVT}
}

\newglossaryentry{vhf}{
  type=\acronymtype,
  name={VHF},
  description={Very high frequency},
  first={VHF (very high frequency)},
  sort={VHF},
  long={very high frequency},
  short={VHF}
}

\newglossaryentry{uhf}{
  type=\acronymtype,
  name={UHF},
  description={Ultra high frequency},
  first={UHF (ultra high frequency)},
  sort={UHF},
  long={ultra high frequency},
  short={UHF}
}

\newglossaryentry{snr}{
  type=\acronymtype,
  name={SNR},
  description={Signal-to-noise ratio},
  first={SNR (signal-to-noise ratio)},
  sort={SNR},
  long={signal-to-noise ratio},
  short={SNR}
}

\newglossaryentry{cdma}{
  type=\acronymtype,
  name={CDMA},
  description={Code division multiple access},
  first={CDMA (code division multiple access)},
  sort={CDMA},
  long={code division multiple access},
  short={CDMA}
}

\newglossaryentry{pr}{
  type=\acronymtype,
  name={PR},
  description={Pseudorandom},
  first={PR (pseudorandom)},
  sort={PR},
  long={pseudorandom},
  short={PR}
}

\newglossaryentry{los}{
  type=\acronymtype,
  name={LOS},
  description={Line of sight},
  first={LOS (line-of-sight)},
  sort={LOS},
  long={line of sight},
  short={LOS}
}

\newglossaryentry{psd}{
  type=\acronymtype,
  name={PSD},
  description={Power spectral density},
  first={power spectral density (PSD)},
  sort={PSD},
  long={power spectral density},
  short={PSD}
}

\newglossaryentry{rf-fe}{
  type=\acronymtype,
  name={RF-FE},
  description={Radio frequency front end},
  first={radio frequency front end (RF-FE)},
  sort={RF-FE},
  long={radio frequency front end},
  short={RF-FE}
}

\newglossaryentry{rf}{
  type=\acronymtype,
  name={RF},
  description={Radio frequency},
  first={RF (radio frequency)},
  sort={RF},
  long={radio frequency},
  short={RF}
}

\newglossaryentry{lna}{
  type=\acronymtype,
  name={LNA},
  description={Low noise amplifier},
  first={LNA (low noise amplifier)},
  sort={LNA},
  long={low noise amplifier},
  short={LNA}
}

\newglossaryentry{adc}{
  type=\acronymtype,
  name={ADC},
  description={Analog-to-digital converter},
  first={ADC (analog-to-digital converter)},
  sort={ADC},
  long={Analog-to-digital converter},
  short={ADC}
}

\newglossaryentry{agc}{
  type=\acronymtype,
  name={AGC},
  description={Automatic gain control},
  first={automatic gain control (AGC)},
  sort={AGC},
  long={automatic gain control},
  short={AGC}
}

\newglossaryentry{lo}{
  type=\acronymtype,
  name={LO},
  description={Local oscillator},
  first={local oscillator (LO)},
  sort={LO},
  long={local oscillator},
  short={LO}
}

\newglossaryentry{sdr}{
  type=\acronymtype,
  name={SDR},
  description={Software-defined radio},
  first={software-defined radio (SDR)},
  sort={SDR},
  long={software-defined radio},
  short={SDR}
}

\newglossaryentry{if}{
  type=\acronymtype,
  name={IF},
  description={Intermediate frequency},
  first={IF (intermediate frequency)},
  sort={IF},
  long={intermediate frequency},
  short={IF}
}

\newglossaryentry{nco}{
  type=\acronymtype,
  name={NCO},
  description={Numerically-controlled oscillator},
  first={NCO (numerically-controlled oscillator)},
  sort={NCO},
  long={numerically-controlled oscillator},
  short={NCO}
}

\newglossaryentry{lpf}{
  type=\acronymtype,
  name={LPF},
  description={Lowpass filter},
  first={lowpass filter (LPF)},
  sort={LPF},
  long={lowpass filter},
  short={LPF}
}

\newglossaryentry{qpsk}{
  type=\acronymtype,
  name={QPSK},
  description={Quadrature phase-shift keying},
  first={quadrature phase-shift keying (QPSK)},
  sort={QPSK},
  long={quadrature phase-shift keying},
  short={QPSK}
}

\newglossaryentry{boc}{
  type=\acronymtype,
  name={BOC},
  description={Binary offset carrier},
  first={BOC (binary offset carrier)},
  sort={BOC},
  long={binary offset carrier},
  short={BOC}
}

\newglossaryentry{altboc}{
  type=\acronymtype,
  name={AltBOC},
  description={Alternative BOC},
  first={AltBOC (alternative BOC)},
  sort={AltBOC},
  long={alternative BOC},
  short={AltBOC}
}

\newglossaryentry{csk}{
  type=\acronymtype,
  name={CSK},
  description={Code sift key},
  first={CSK (code sift key)},
  sort={CSK},
  long={code sift key},
  short={CSK}
}

\newglossaryentry{wss}{
  type=\acronymtype,
  name={WSS},
  description={Wide-sense stationary},
  first={wide-sense stationary (WSS)},
  sort={WSS},
  long={wide-sense stationary},
  short={WSS}
}

\newglossaryentry{pdf}{
  type=\acronymtype,
  name={PDF},
  description={Probability density function},
  first={probability density function (PDF)},
  sort={PDF},
  long={probability density function},
  short={PDF}
}

\newglossaryentry{cdf}{
  type=\acronymtype,
  name={CDF},
  description={Cumulative distribution function},
  first={cumulative distribution function (CDF)},
  sort={CDF},
  long={cumulative distribution function},
  short={CDF}
}

\newglossaryentry{ppp}{
  type=\acronymtype,
  name={PPP},
  description={Precise point positioning},
  first={precise point positioning (PPP)},
  sort={PPP},
  long={precise point positioning},
  short={PPP}
}

\newglossaryentry{rtk}{
  type=\acronymtype,
  name={RTK},
  description={Real-time kinematics},
  first={real-time kinematics (RTK)},
  sort={RTK},
  long={real-time kinematics},
  short={RTK}
}

\newglossaryentry{scap}{
  type=\acronymtype,
  name={SCAp},
  description={Safety- and liability-critical applications},
  first={SCAp (safety- and liability-critical applications)},
  sort={SCAp},
  long={safety- and liability-critical applications},
  short={SCAp}
}

\newglossaryentry{ism}{
  type=\acronymtype,
  name={ISM},
  description={Ionospheric scintillation monitoring},
  first={ionospheric scintillation monitoring (ISM)},
  sort={ISM},
  long={ionospheric scintillation monitoring},
  short={ISM}
}

\newglossaryentry{tcxo}{
  type=\acronymtype,
  name={TCXO},
  description={Temperature compensated crystal oscillator},
  first={TCXO (temperature compensated crystal oscillator)},
  sort={TCXO},
  long={temperature compensated crystal oscillator},
  short={TCXO}
}

\newglossaryentry{ocxo}{
  type=\acronymtype,
  name={OCXO},
  description={Oven-controlled crystal oscillator},
  first={OCXO (oven-controlled crystal oscillator)},
  sort={OCXO},
  long={oven-controlled crystal oscillator},
  short={OCXO}
}

\newglossaryentry{gps}{
  type=\acronymtype,
  name={GPS},
  description={Global positioning system},
  first={GPS (global positioning system)},
  sort={GPS},
  long={global positioning system},
  short={GPS}
}

\newglossaryentry{mf}{
  type=\acronymtype,
  name={MF},
  description={Multifrequency.},
  first={multifrequency (MF)},
  sort={MF},
  long={multifrequency},
  short={MF}
}

\newglossaryentry{mc}{
  type=\acronymtype,
  name={MC},
  description={Multiconstellation.},
  first={multiconstellation (MC)},
  sort={MC},
  long={multiconstellation},
  short={MC}
}

\newglossaryentry{pe}{
  type=\acronymtype,
  name={PE},
  description={Parabolic equation.},
  first={parabolic equation (PE)},
  sort={PE},
  long={parabolic equation},
  short={PE}
}

\newglossaryentry{tec}{
  type=\acronymtype,
  name={TEC},
  description={Total electron content.},
  first={TEC (total electron content)},
  sort={TEC},
  long={total electron content},
  short={TEC}
}

\newglossaryentry{gism}{
  type=\acronymtype,
  name={GISM},
  description={Global ionospheric scintillation model.},
  first={global ionospheric scintillation model (GISM)},
  sort={GISM},
  long={global ionospheric scintillation model},
  short={GISM}
}

\newglossaryentry{np}{
  type=\acronymtype,
  name={NP},
  description={Neyman-Pearson detector.},
  first={Neyman-Pearson (NP)},
  sort={NP},
  long={Neyman-Pearson detector},
  short={NP}
}

\newglossaryentry{cn0}{
  type=\acronymtype,
  name={\(C/N_0\)},
  description={Carrier-to-noise ratio.},
  first={carrier-to-noise ratio (\(C/N_0\))},
  sort={C/N_0},
  long={carrier-to-noise ratio},
  short={\(C/N_0\)}
}

\newglossaryentry{svm}{
  type=\acronymtype,
  name={SVM},
  description={Support vector machine.},
  first={support vector machine (SVM)},
  sort={SVM},
  long={support vector machine},
  short={SVM}
}

\newglossaryentry{ca}{
  type=\acronymtype,
  name={C/A},
  description={Coarse/acquisition.},
  first={C/A (coarse/acquisition)},
  sort={C/A},
  long={coarse/acquisition},
  short={C/A}
}

\newglossaryentry{acf}{
  type=\acronymtype,
  name={ACF},
  description={Autocorrelation function.},
  first={autocorrelation function (ACF)},
  sort={ACF},
  long={autocorrelation function},
  short={ACF}
}

\newglossaryentry{pll}{
  type=\acronymtype,
  name={PLL},
  description={Phase-locked loop.},
  first={phase-locked loops (PLLs)},
  sort={PLL},
  long={phase-locked loop},
  plural={phase-locked loops},
  short={PLL}
}

\newglossaryentry{dll}{
  type=\acronymtype,
  name={DLL},
  description={delay-locked loop.},
  first={delay-locked loops (DLLs)},
  sort={DLL},
  long={delay-locked loop},
  plural={delay-locked loops},
  short={DLL}
}

\newglossaryentry{ar}{
  type=\acronymtype,
  name={AR},
  description={Autoregressive.},
  first={AR (autoregressive)},
  sort={AR},
  long={autoregressive},
  plural={autoregressive},
  short={AR}
}

\newglossaryentry{csm}{
  type=\acronymtype,
  name={CSM},
  description={Cornell scintillation model.},
  first={CSM (Cornell scintillation model)},
  sort={CSM},
  long={Cornell scintillation model},
  plural={Cornell scintillation model},
  short={CSM}
}

\newglossaryentry{asic}{
  type=\acronymtype,
  name={ASIC},
  description={Application-specific integrated circuit.},
  first={application-specific integrated circuits (ASICs)},
  sort={ASIC},
  long={application-specific integrated circuit},
  plural={application-specific integrated circuits},
  short={ASICs}
}

\newglossaryentry{up}{
  type=\acronymtype,
  name={\textmu P},
  description={Microprocessor.},
  first={microprocessors (\textmu Ps)},
  sort={\textmu P},
  long={microprocessor},
  plural={microprocessors},
  short={\textmu Ps}
}

\newglossaryentry{ml}{
  type=\acronymtype,
  name={ML},
  description={Maximum likelihood.},
  first={maximum likelihood (ML)},
  sort={ML},
  long={maximum likelihood},
%   plural={},
  short={ML}
}

\newglossaryentry{cnn}{
  type=\acronymtype,
  name={CNN},
  description={Convolutional neural network.},
  first={convolutional neural network (CNN)},
  sort={CNN},
  long={convolutional neural network},
  plural={convolutional neural networks},
  short={CNN}
}

\newglossaryentry{tsc}{
  type=\acronymtype,
  name={TSC},
  description={Time series classification.},
  first={time series classification (TSC)},
  sort={TSC},
  long={time series classification},
  short={TSC}
}


\newglossaryentry{dtw}{
  type=\acronymtype,
  name={DTW},
  description={Dynamic time warping.},
  first={dynamic time warping (DTW)},
  sort={DTW},
  long={dynamic time warping},
%   plural={application-specific integrated circuits},
  short={DTW}
}

\newglossaryentry{nn}{
  type=\acronymtype,
  name={NN},
  description={Nearest neighbour},
  first={NN (nearest neighbour)},
  sort={NN},
  long={nearest neighbour},
%   plural={application-specific integrated circuits},
  short={NN}
}

\newglossaryentry{svc}{
  type=\acronymtype,
  name={SVC},
  description={Support vector classifier.},
  first={support vector classifier (SVC)},
  sort={SVC},
  long={support vector classifier},
  short={SVC}
}

\newglossaryentry{stft}{
  type=\acronymtype,
  name={STFT},
  description={Short-time Fourier transform.},
  first={short-time Fourier transform (STFT)},
  sort={STFT},
  long={short-time Fourier transform},
  short={STFT}
}

\newglossaryentry{pca}{
  type=\acronymtype,
  name={PCA},
  description={Principal component analysis (PCA).},
  first={principal component analysis (PCA)},
  sort={PCA},
  long={principal component analysis},
  short={PCA}
}

\newglossaryentry{svd}{
  type=\acronymtype,
  name={SVD},
  description={Singular value decomposition.},
  first={SVD (singular value decomposition)},
  sort={SVD},
  long={singular value decomposition},
  short={SVD}
}

\newglossaryentry{evd}{
  type=\acronymtype,
  name={EVD},
  description={Eigenvalue decomposition.},
  first={EVD (eigenvalue decomposition)},
  sort={EVD},
  long={eigenvalue decomposition},
  short={EVD}
}

\newglossaryentry{dl}{
  type=\acronymtype,
  name={DL},
  description={Deep learning.},
  first={deep learning (DL)},
  sort={DL},
  long={deep learning},
  short={DL}
}

\newglossaryentry{mlp}{
  type=\acronymtype,
  name={MLP},
  description={Multilayer perceptron.},
  first={multilayer perceptron (MLP)},
  sort={MLP},
  long={multilayer perceptron},
%   plural={},
  short={MLP}
}

\newglossaryentry{wscs}{
  type=\acronymtype,
  name={WSCS},
  description={Wide-sense cyclostationary.},
  first={wide-sense cyclostationary (WSCS)},
  sort={WSCS},
  long={wide-sense cyclostationary},
  %   plural={},
  short={WSCS}
}

\newglossaryentry{itu}{
  type=\acronymtype,
  name={ITU},
  description={International Telecommunications Union.},
  first={International Telecommunications Union (ITU)},
  sort={ITU},
  long={International Telecommunications Union},
  %   plural={},
  short={ITU}
}

\newglossaryentry{mse}{
  type=\acronymtype,
  name={MSE},
  description={Mean squared error.},
  first={mean squared error (MSE)},
  sort={MSE},
  long={mean squared error},
  %   plural={},
  short={MSE}
}

\newglossaryentry{mvu}{
  type=\acronymtype,
  name={MVU},
  description={Minimum variance unbiased.},
  first={minimum variance unbiased (MVU)},
  sort={MVU},
  long={minimum variance unbiased},
  %   plural={},
  short={MVU}
}

\newglossaryentry{crb}{
  type=\acronymtype,
  name={CRB},
  description={Cramér-Rao bound.},
  first={Cramér-Rao bound (CRB)},
  sort={CRB},
  long={Cramér-Rao bound},
  %   plural={},
  short={CRB}
}

\newglossaryentry{bcrb}{
  type=\acronymtype,
  name={BCRB},
  description={Baysean Cramér-Rao.},
  first={Baysean Cramér-Rao (BCRB)},
  sort={BCRB},
  long={Baysean Cramér-Rao},
  %   plural={},
  short={BCRB}
}

\newglossaryentry{dnn}{
  type=\acronymtype,
  name={DNN},
  description={Deep Neural Network.},
  first={deep neural network (DNN)},
  sort={DNN},
  long={deep neural network},
  %   plural={},
  short={DNN}
}

\newglossaryentry{ann}{
  type=\acronymtype,
  name={ANN},
  description={Artificial Neural Networks.},
  first={artificial neural networks (ANN)},
  sort={ANN},
  long={artificial neural networks},
  %   plural={},
  short={ANN}
}

\newglossaryentry{ai}{
  type=\acronymtype,
  name={AI},
  description={Artificial Intelligence.},
  first={artificial intelligence (AI)},
  sort={AI},
  long={artificial intelligence},
  %   plural={},
  short={AI}
}

\newglossaryentry{sgd}{
  type=\acronymtype,
  name={SGD},
  description={Stochastic gradient descent.},
  first={stochastic gradient descent (SGD)},
  sort={SGD},
  long={stochastic gradient descent},
  %   plural={},
  short={SGD}
}

\newglossaryentry{bpnn}{
  type=\acronymtype,
  name={BPNN},
  description={Backpropagation neural network.},
  first={backpropagation neural network (BPNN)},
  sort={BPNN},
  long={backpropagation neural network},
  %   plural={},
  short={BPNN}
}

\newglossaryentry{rbf}{
  type=\acronymtype,
  name={RBF},
  description={Radial basis function.},
  first={radial basis function (RBF)},
  sort={RBF},
  long={radial basis function},
  %   plural={},
  short={RBF}
}

\newglossaryentry{ols}{
  type=\acronymtype,
  name={OLS},
  description={Ordinary Least Squares.},
  first={ordinary least squares (OLS)},
  sort={OLS},
  long={Ordinary Least Squares},
  %   plural={},
  short={OLS}
}

\newglossaryentry{rls}{
  type=\acronymtype,
  name={RLS},
  description={Recursive Least Squares.},
  first={recursive least squares (RLS)},
  sort={RLS},
  long={recursive least squares},
  %   plural={},
  short={RLS}
}

\newglossaryentry{lms}{
  type=\acronymtype,
  name={LMS},
  description={Least Mean Squares.},
  first={least mean squares (LMS)},
  sort={LMS},
  long={least mean squares},
  %   plural={},
  short={LMS}
}

\newglossaryentry{sde}{
  type=\acronymtype,
  name={SDE},
  description={Stochastic differential equation.},
  first={stochastic differential equation (SDE)},
  sort={SDE},
  long={stochastic differential equation},
  longplural={stochastic differential equations},
  short={SDE}
}

\newglossaryentry{ode}{
  type=\acronymtype,
  name={ODE},
  description={Ordinary differential equation.},
  first={ordinary differential equation (ODE)},
  sort={ODE},
  long={ordinary differential equation},
  longplural={ordinary differential equations},
  short={ODE}
}

\newglossaryentry{dae}{
  type=\acronymtype,
  name={DAE},
  description={Differential-algebraic system of equations.},
  first={differential-algebraic system of equations (DAE)},
  sort={DAE},
  long={differential-algebraic system of equations},
  short={DAE}
}

\newglossaryentry{rms}{
  type=\acronymtype,
  name={RMS},
  description={Root mean square.},
  first={root mean square (RMS)},
  sort={RMS},
  long={root mean square},
  short={RMS}
}

\newglossaryentry{lut}{
  type=\acronymtype,
  name={LUT},
  description={Lookup table.},
  first={LUT (lookup table)},
  sort={LUT},
  long={lookup table},
  longplural={lookup tables},
  short={LUT}
}

\newglossaryentry{fir}{
  type=\acronymtype,
  name={FIR},
  description={Finite impulse response.},
  first={finite impulse response (FIR)},
  sort={FIR},
  long={finite impulse response},
  short={FIR}
}

\newglossaryentry{isi}{
  type=\acronymtype,
  name={ISI},
  description={Intersymbol interference.},
  first={intersymbol interference (ISI)},
  sort={ISI},
  long={intersymbol interference},
  short={ISI}
}

\newglossaryentry{lsb}{
  type=\acronymtype,
  name={LSB},
  description={Least significant bit.},
  first={least significant bit (LSB)},
  sort={LSB},
  long={least significant bit},
  short={LSB}
}

\newglossaryentry{msb}{
  type=\acronymtype,
  name={MSB},
  description={Most significant bit.},
  first={most significant bit (MSB)},
  sort={MSB},
  long={most significant bit},
  short={MSB}
}

\newglossaryentry{bb}{
  type=\acronymtype,
  name={BB},
  description={Baseband.},
  first={baseband (BB)},
  sort={BB},
  long={baseband},
  short={BB}
}